---
title: "Lab11_PatrickIhejirika"
author: "Patrick Ihejirika"
date: "12/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)
An X and Y variable contain the above numbers.

A. Compute Pearson’s r and report the associated p-value using the cor.test() function. (2 points)

```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)
cortest = cor.test(X,Y, method = c("pearson"))
```
The related p value is `r  cortest$p.value`

B. Use a permutation test to create a null-distribution, and report the p-value for getting the observed correlation or larger using your simulated null-distribution. (2 points)

```{r}
sim_rs <- replicate(1000,cor(sample(X),sample(Y)))
hist(sim_rs)

length(sim_rs[sim_rs >= cortest$p.value])/ length(sim_rs)
```

Using the variables X and Y above, and assuming that the values could be re-ordered in any way, report the following:

A. the smallest possible sum of cross-products (1 point)

B. the largest possible sum of cross-products (1 point)



```{r}
#Maximum should be when X and Y are in increasing order
X2 = sort(X, decreasing = FALSE)
Y2 = sort(Y, decreasing = FALSE)
sum(X2*Y2)


#Maximum should be when X and Y are in increasing order
Y3 = sort(Y, decreasing = TRUE)
sum(X2*Y3)
```






